Forecasting short-term hourly Emergency Department arrivals

### 2022-02-09 paper/paper.Rmd
Update fig captions and remove figs 2 and 7

```{r hourly-plot-ridge, fig.cap= "Distrubution of admission per hour and day of the week", fig.align='center',fig.width= 6.5,fig.height=5.5}
```

@@

```{r seasonplot-dofw, fig.cap= "Seasonal plot: day of week arrivals", fig.align='center',out.width="70%"}
```

@@

```{r seasonplot-weekofyear, fig.cap= "Week of year arrivals", fig.align='center',out.width="70%"}
```

@@

```{r date-plot, fig.cap= "Daily arrivals", fig.align='center',out.width="70%"}
```

@@

```{r Pinball, fig.cap= "Pinball loss values over different quantiles.", fig.align='center',out.width= "90%"}
```

@@

```{r quantile-bias, fig.cap= "Quantile bias vs the nominal quantiles.", fig.align='center',out.width= "90%"}
```

@@

```{r Skill-rel2bench-reduced, fig.cap= "Pinball skill score for the seven best performing approaches.", fig.align='center',out.width= "70%"}
```

@@

```{r lead-time-rmse, fig.cap= "RMSE values over the forecast horizon.", fig.align='center',out.width= "70%"}
```

@@

```{r time-accuracy, fig.cap= "Running time vs. forecast accuracy", fig.align='center',out.width= "70%"}
```

>>>>

```{r hourly-plot-ridge, fig.cap= "Distrubution of admission by hour-of-day and day-of-week. Most days have a distinct pattern, such as relatively high arrivals on Monday mornings and in the early hours of Saturday and Sunday morning.", fig.align='center',fig.width= 6.5,fig.height=5.5}
```

@@

<!--- ```{r seasonplot-dofw, fig.cap= "Seasonal plot: day of week arrivals", fig.align='center',out.width="70%"}
``` --->

@@

```{r seasonplot-weekofyear, fig.cap= "Arrivals by week-of-year. There is an annual trend of reduced arrivals durnng the summer and winter holiday period.", fig.align='center',out.width="70%"}
```

@@

```{r date-plot, fig.cap= "Daily arrivals over the entire dataset with moving average trend (blue line) and dates of outliers labled. Low outliers invariables correspond to public holidays.", fig.align='center',out.width="70%"}
```

@@

```{r Pinball, fig.cap= "Pinball loss values by quantile. Benchmark-2, NBI-2 and NOtr-2 have similar performance with most improvement of the latter two over the benchmark comming from the lower quantiles. All other models have a greater Pinball score (worse performance) than Benchmark-2 across all quantiles.", fig.align='center',out.width= "90%"}
```

@@

```{r quantile-bias, fig.cap= "Quantile bias illustrates the difference between the nominal exceedance of prediceted quantiles and the observed frequency of exceedance. If a predictive model is calibrated, quantile bias should be approximately zero accross all probability levels. Here we see that the predictive distributions produced by TBATS are underdispersed (too narrow/over confident); those produced by NBI-2, GBM-2 and Benchmark-2" bias and underpredict accross all probability levels; and that forecasts produced by ADAM-iETSX, NOtr-2 and Prophet are well calibrated.", fig.align='center',out.width= "90%"}
```

@@

<!--
```{r Skill-rel2bench-reduced, fig.cap= "Pinball skill score for the seven best performing approaches.", fig.align='center',out.width= "70%"}
```

@@

```{r lead-time-rmse, fig.cap= "RMSE values over the forecast horizon for forecasts issues at midnight. Attendance during the morning is more challenging to predice resulting in greater RMSE during these hours for all models.", fig.align='center',out.width= "70%"}
```

@@

```{r time-accuracy, fig.cap= "Running time vs. forecast performance", fig.align='center',out.width= "70%"}
```
